### 2018-03-19 paper/sexSelectionSpacing-ver1.tex
Add example graphs for how sex ratio change within spell

The results so far show that as sex ratios have become more
male-biased the spacing when a woman has only girls have become 
longer relative to other sex compositions, presumably because
of increased use of sex selection rather than because of a
change in the degree of son preference.
Neither the median spacing or the conditional survival curves
can, however, provide us with information on how the use of
sex selection vary \emph{within} a spell.
Furthermore, using conditional survival curves forces everybody 
to finish the spell in the same month and does not provide
any information about how many births there are.
We can, however, learn something about both changes in 
sex selection within a spell and the likelihood of exiting
with a birth using standard  survival curves.

@@

The flatter the curve the fewer births.

@@

% High education

\begin{figure}[htpb]
\centering
\caption*{First child a girl}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=2,689)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_g_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=4,869)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_g_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=3,774)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First child a boy}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,806)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_high_urban_b_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=5,246)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_high_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=3,969)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_b_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after first birth for urban 
women with 8 or more years of education by month beginning 9 months after prior birth. 
Predictions based on age 22 at first birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell2_high_urban}
\end{figure}

>>>>

The results so far show that as sex ratios became more
male-biased the spacing when a woman has only girls became 
longer relative to other sex compositions, presumably because
of increased use of sex selection rather than a reduction in son preference.
Neither the median spacing or the conditional survival curves
can, however, provide us with information on how the use of
sex selection vary \emph{within} a spell.
Furthermore, using conditional survival curves forces everybody 
to finish the spell in the same month and does not provide
any information about how many births there are.
We can, however, learn something about both changes in 
sex selection within a spell and the likelihood of exiting
with a birth using standard  survival curves.

The predicted sex ratio may change within a spell for, at
least, two reasons.
First, parents may stop using prenatal sex determination 
once the duration from the previous birth becomes long enough
because they prefer not to have their children too far apart.
In this case we should observe the predicted sex ratio decline
with spell length.
Second, if the degree of son preference vary within the sample
but behavior is not affected by duration from the previous birth,
we should observe an increasing share of births come from 
parents with stronger son preference as duration from the
previous birth increases.
Whereas the early births are a combination of births to
people with lower son preference and those with stronger son
preference who conceived a son in the first or second pregnancy,
later births are then predominately from those with stronger
son preference who have not yet conceived a son.
Hence, in this case we should see an increase in the sex ratio 
as duration increases.

% Examples of declining sex ratios

\begin{figure}[htpb!]
\centering
\rotatebox[origin=c]{90}{\footnotesize{Urban}}
\setcounter{subfigure}{-2}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_urban_g_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_urban_g_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{Rural}}
\setcounter{subfigure}{0}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_high_rural_g_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_high_rural_g_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\caption{Predicted probability of having a boy and probability of 
no birth yet from nine months after first birth for women with a girl
as their first child and eight or more years of education 
for the 1995--2004 and 2005--2016 periods
} 
\label{fig:decreasing_sex_ratio} 
\end{figure}

% Examples of increasing sex ratios

\begin{figure}[htpb!]
\centering
\rotatebox[origin=c]{90}{\footnotesize{First children 2 girls}}
\setcounter{subfigure}{-2}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{-1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_urban_gg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\footnotesize{First children 1 boy and 1 girl}}
\setcounter{subfigure}{0}
\subfloat[1995--2004]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_high_rural_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\setcounter{subfigure}{1}
\subfloat[2005--2016]{
   \begin{minipage}{0.39\textwidth}
       \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
       \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_pc}}\\
       \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_high_rural_bg_s}}
       \captionsetup[subfigure]{labelformat=parens}
   \end{minipage}
}
\caption{Predicted probability of having a boy and probability of 
no birth yet from nine months after second birth for urban women with
eight or more years of education 
for the 1995--2004 and 2005--2016 periods
} 
\label{fig:decreasing_sex_ratio} 
\end{figure}

@@

@@
